CODECHECK: An open-science initiative for the independent execution of computations underlying research articles.

### 2021-01-08 codecheck-paper.tex
fix latex error
questions marks denote waiting to hear from person

\begin{enumerate}
\item Check with Giuliano re: ``code works''.
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
\item \url{https://av.tib.eu/media/42484} > "Code will make systematic mistakes, not random mistakes", "code is more reliable (and auditable) than a human"
\item \url{https://doi.org/10.1016/j.isci.2020.101698} - "Rigor and Transparency Index may serve as a proxy for methodological quality" - CODECHECK doesn't evaluate that, could be used for distinction
\item Make code Feedback and leave better than found a principle, not an option? Just checking the code does not give enough credit (?), but improving it certainly does, and good peer review improves (watch out to not do full software review though)
\end{itemize}

@@

We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison, Giuliano
Maciocci, Naomi Penfold (eLife), Rebecca Kirk (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton (Scientific Data). Iain Davies and
Yuhao (Sebastian) Wang developed code and example certificates.
We thank Antonio P\'{a}ez (Journal of Geographical Systems) for enabling
CODECHECKs, Carlos Granell and Frank Ostermann for contributing
certificates as reproducibility reviewers at the AGILE conference, and 
all authors of auditable workflows for their participation.

>>>>

\begin{enumerate}
\item Check with Giuliano re: ``code works''.
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Should we ask the people currently listed in the acknowledgements?
\item revisit \url{https://github.com/codecheckers/discussion}
\item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
\item \url{https://av.tib.eu/media/42484} > "Code will make systematic mistakes, not random mistakes", "code is more reliable (and auditable) than a human"
\item \url{https://doi.org/10.1016/j.isci.2020.101698} - "Rigor and Transparency Index may serve as a proxy for methodological quality" - CODECHECK doesn't evaluate that, could be used for distinction
\item Make code Feedback and leave better than found a principle, not an option? Just checking the code does not give enough credit (?), but improving it certainly does, and good peer review improves (watch out to not do full software review though)
\end{enumerate}

@@

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings?, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold? (eLife), Rebecca Kirk? (PLOS Computational Biology), Scott
Edmunds (GigaScience), and Andrew Hufton? (Scientific Data). Iain Davies? and
Yuhao (Sebastian) Wang? developed code and example certificates.
We thank Antonio P\'{a}ez? (Journal of Geographical Systems) for enabling
CODECHECKs, Carlos Granell? and Frank Ostermann? for contributing
certificates as reproducibility reviewers at the AGILE conference, and 
all authors of auditable workflows for their participation.
